Quality of Service with Software Defined Network.

### 2017-03-05 report/paper.tex
Continued report

    \#TODO MATTEO
    \subsubsection{Trougthput}
    \#TODO andrea
    \subsubsection{Link Capacity}
    \#TODO andrea
    \subsubsection{altre}
    \#TODO andrea

  \subsection{Route changing} %cambio rotte
  \#TODO andrea

@@

  \subsection{Ip switching in pox}
  \#TODO andrea

>>>>

    \#TODO MATTEO
		\subsubsection{Link Capacity}
		\#TODO andrea
		The first data that was collected was the actual link capacity, which depends both on the cable used to connect
		different devices and the effective capacity for each ethernet port linked by the cable itself. Everytime a device supporting
		openflow connects to the controller, it gives to the latter information about its status and its capabilities. One of them is
		the link capacity in three ways: the first is the \textit{supported} capacity, which is the phisical maximum capacity, the second is the
		\textit{advised} capacity, which name describes itself and the latter is the \textit{current} one. We choose to save the last one,
		as it gives the most useful about the link state. This information, moreover, is the one that non-SDN switches use to choose the \textit{metric}
		parameter. The simulation with Mininet showed us that this type of information can be used, but the Routeboards didn't support it.
		As a matter of fact, we weren't able to exploit this capacity in our network realization.
    \subsubsection{Throughput}
    \#TODO andrea
		Using the flow statistics, we analyzed the traffic going through a link and, with a simple division, we got the normalized throughput.
		We exploited the information given by the switches with the match structure: this means that we used the throughput for the TCP traffic,
		the one for the UDP and for each of them we could know toward which IP the traffic is directed or is from. This was exploited with mininet
		simulations, but not in the set up in the laboratory. With the latter, we used the statistics as an indicator of the bitrate of a link
		and divided the host to categories based on it.

		\subsubsection{Packet error rate}
		The port statistics given by the switches contains different informations about the state of each port in a switch. To classify a link for its
		reliability, we divided the number of packets with erroneous symbols that couldn't be corrected with a FEC by the total number of packets that were sent,
		getting the packet error rate. The choice we made when exploiting this statistic was privileging the gaming and normal traffic, wherease the
		heavy traffic was directed to links with highest packet error rate.
		\#TODO andrea

    \subsubsection{altre}
    \#TODO andrea ?!?!?

  \subsection{Route changing} %cambio rotte
  \#TODO andrea
	For each statistic we got and each parameter we obtained, we changed the weight of the graphs. Every graph we used had a specific weight, so the
	Dijkstra algorithm for a weighted graph gave different minimum path between two hosts. From the parameter we saved, we choose to change the
	route to reach the destination and viceversa. The traffic follow the same path, in both the directions and depends only on the type of traffic:
	we choose to set the minimum unweighted path if no statistics were available, the minimum throughput path for the standard traffic, the minimum
	delay for the gaming one and the maximum packet error rate for the heavy traffic generated by a host.
	The changing of the path were made only if the last change happened before one minute because the torrent traffic has, in its protocol, a discovery
	algortithm. This means that if a lot of changes were made, most of the traffic generated by the peer to peer, is the control one and the result is that the
	load in the network will be heavy and last longer.

@@

  \subsection{Ip switching in pox}
  \#TODO andrea
	One of the problem encountered was that, if an host is already found by pox and there is a PacketIn event, the core of the controller
	switches the source and the destination IP and MAC address with the source one. The problem was partially solved, checking out the
	parameters known by the controller, i.e. if the two host are connected to two different switches and the controller switches the source with the
	destination address, we can switch it back; the result is that the PacketIn event now has correct informations.
